# Data

## Description

The primary dataset for this project is sourced from the **`appa` R package**, created by Avery Robbins and available on GitHub ([appa repository](https://github.com/averyrobbins1/appa/tree/master)). The original data was scraped from two online sources:[Avatar Wiki](https://avatar.fandom.com/wiki/Avatar_Wiki) and  [IMDb](https://www.imdb.com/title/tt0417299/?ref_=fn_al_tt_2). The `appa` GitHub repository includes the R scripts used to perform the web scraping, offering transparency in the data collection process.

The dataset is structured as a table containing **13,385 rows** and **12 columns**, where each row corresponds to a character line or a scene description from the TV show *Avatar: The Last Airbender*. Below are the variables and their descriptions:

| Variable           | Class       | Description                                      |
|--------------------|-------------|--------------------------------------------------|
| `id`               | Integer     | Unique row identifier.                          |
| `book`             | Factor      | Book name (e.g., "Water", "Earth").             |
| `book_num`         | Integer     | Book number (1 for "Water", 2 for "Earth", etc.).|
| `chapter`          | Factor      | Chapter name.                                   |
| `chapter_num`      | Integer     | Chapter number within a book.                  |
| `character`        | Character   | Name of the character speaking.                |
| `full_text`        | Character   | Full text (scene description or character text).|
| `character_words`  | Character   | Text spoken by characters.                     |
| `writer`           | Character   | Writer(s) of the episode.                      |
| `director`         | Character   | Director(s) of the episode.                    |
| `imdb_rating`      | Double      | IMDb rating of the episode.                    |


The dataset was last updated on **June 6, 2020**. While the underlying content from the TV show remains unchanged since its conclusion in **July 2008**, IMDb ratings may have fluctuated over time due to ongoing audience reviews. 

To access the data, users can install the **`appa` R package** from GitHub using the following commands:

```{r}
devtools::install_github("averyrobbins1/appa")
dat <- appa::appa
```



## Missing value analysis
```{r}
library(dplyr)
dat <- appa::appa
glimpse(dat)
```

