# Data

## Description

The primary dataset for this project is sourced from the **`appa` R package**, created by Avery Robbins and available on GitHub ([appa repository](https://github.com/averyrobbins1/appa/tree/master)). The original data was scraped from two online sources: [Avatar Wiki](https://avatar.fandom.com/wiki/Avatar_Wiki) and [IMDb](https://www.imdb.com/title/tt0417299/?ref_=fn_al_tt_2). The `appa` GitHub repository includes the R scripts used to perform the web scraping, offering transparency in the data collection process.

The dataset is structured as a table containing **13,385 rows** and **12 columns**, where each row corresponds to a character line or a scene description from the TV show *Avatar: The Last Airbender*. Below are the variables and their descriptions:

| Variable           | Class       | Description                                      |
|--------------------|-------------|--------------------------------------------------|
| `id`               | Integer     | Unique row identifier.                          |
| `book`             | Factor      | Book name (e.g., "Water", "Earth").             |
| `book_num`         | Integer     | Book number (1 for "Water", 2 for "Earth", etc.).|
| `chapter`          | Factor      | Chapter name.                                   |
| `chapter_num`      | Integer     | Chapter number within a book.                  |
| `character`        | Character   | Name of the character speaking.                |
| `full_text`        | Character   | Full text (scene description or character text).|
| `character_words`  | Character   | Text spoken by characters.                     |
| `writer`           | Character   | Writer(s) of the episode.                      |
| `director`         | Character   | Director(s) of the episode.                    |
| `imdb_rating`      | Double      | IMDb rating of the episode.                    |


The dataset was last updated on **June 6, 2020**. While the underlying content from the TV show remains unchanged since its conclusion in **July 2008**, IMDb ratings may have fluctuated over time due to ongoing audience reviews.

Another issue with the data is that the `character` column may list multiple characters in a single row. If we aim to measure which character speaks the most, this column will require additional preprocessing to split and appropriately attribute the dialogue to each individual character.

Additionally, if we want to create statistics based on character-specific attributes, such as age or gender, this information is not present in the dataset and will need to be obtained and integrated from an external source.

To access the data, users can install the **`appa` R package** from GitHub using the following commands:

```{r}
devtools::install_github("averyrobbins1/appa")
dat <- appa::appa
```



## Missing value analysis
```{r,message=FALSE}
library(dplyr)
library(ggplot2)
library(redav)
dat <- appa::appa
plot_missing(dat,max_cols = 5)
```

Notice that the missing values appear only in two columns: `character_words` and `imdb_rating`. In most cases, only `character_words` is missing, which suggests that there is no clear pattern connecting these missing values.

However, as shown in the following graph, the missing values in `character_words` occur when no characters are speaking, and the `full_text` refers to a scene description rather than a dialogue.
```{r}
ggplot(dat |> group_by(character) |> 
  summarise(Missing_dialogue=sum(is.na(character_words)/n())) |> 
  arrange(desc(Missing_dialogue)) |> 
  head(10),
  aes(y=character,x=Missing_dialogue))+geom_col(fill="blue")+
  scale_x_continuous(labels = scales::percent,limits = c(0,1.05)) +
  labs(x = "Missing Dialogue (%)", y = "Character") +
  theme_minimal()+
  geom_text(aes(label = scales::percent(Missing_dialogue)), 
            hjust = -0.1, color = "black")+
  ggtitle("Top 10 Characters with Missing Dialogues")
```
Regarding the `imdb_rating` column, the next graph illustrates that the missing values correspond to only one episode. This explains why the proportion of missing values in `imdb_rating` is very small in the initial graph.
```{r}
ggplot(dat |> group_by(chapter) |> 
  summarise(Missing_rating=sum(is.na(imdb_rating)/n())) |> 
  arrange(desc(Missing_rating)) |> 
  head(10),
  aes(y=chapter,x=Missing_rating))+geom_col(fill="blue")+
  scale_x_continuous(labels = scales::percent,limits = c(0,1.05)) +
  labs(x = "Missing Rating (%)", y = "Episode") +
  theme_minimal()+
  geom_text(aes(label = scales::percent(Missing_rating)), 
            hjust = -0.1, color = "black")+
  ggtitle("Top 10 Episodes without IMDb Rating")
```

In conclusion, these missing values are unlikely to significantly impact our analysis. The missing `character_words` values align with scene descriptions, which are not central to dialogue-based metrics, and the single missing `imdb_rating` affects only one episode, representing a negligible proportion of the data.
